Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-08-16 article.tex
Better estimate of computational scaling to all of aLIGO; more realistic flop/s numbers
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1352 ccdd05d5-56c1-461a-bf98-85f6876523b4

Table~\ref{table:flops} shows that the \lloid\ method requires $6.6 \times 10^8$
\flops\ to cover a sub-bank comprising 657 out of the total 98544
mass pairs.  Given that modern (ca. 2011) workstations can sustain computation
rates up to $\sim$$10^{10}$~\flops{}, and assuming that other regions of the
parameter space have similar computational scaling, an entire single detector
search for \NS--\NS\ signals in the 1--3~$M_\odot$ component mass range could be
implemented with $\sim$$10^{11}$ \flops\, or $\sim$$10$ machines.

@@

This paper has \LIGO\ Document Number {LIGO-P0900004-v26}.

>>>>

Table~\ref{table:flops} shows that the \lloid\ method requires $6.6 \times 10^8$
\flops\ to cover a sub-bank comprising 657 out of the total 98544 mass pairs.
Assuming that other regions of the parameter space have similar computational
scaling, an entire single detector search for \NS--\NS\ signals in the
1--3~$M_\odot$ component mass range could be implemented with
$\sim$$10^{11}$~\flops.  Modern (ca. 2011) workstations can achieve peak
computation rates up to $\sim$$10^{11}$~\flops.  In practice, we expect that a
software implementation of \lloid\ will reach average computation rates that are
perhaps a factor 10 less than this, $\sim$$10^{10}$~\flops\ per machine, due to
non-floating point tasks including bookkeeping and thread synchronization.
Given these considerations, we estimate that a full single-detector Advanced
\LIGO\ search with \lloid\ will require about $\sim$$10$ machines.

@@

This paper has \LIGO\ Document Number {LIGO-P0900004-v27}.
